FraCaS: 80 percent complete

### 2019-02-28 paper2018/paper.tex
clean and compress
compress

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types. Coq is  one of the leading proof
assistants. It has famously been instrumental in formalising a proof
of the four-color theorem \citep{Gonthier:2008}, a proof of the odd
order theorem \citep{Gonthier:2013}. Coq is a very powerful
reasoning engine that makes it fit for the task of NLI, when the
latter is formalized as theorem proving task. It involves a very higher order logic  and supports a number of constructions, notably dependent typing and subtyping, that are instrumental in expressing NL semantics.

@@

Our system consists of two main parts.
\begin{enumerate}
\item A converter from syntax trees to types. The syntax trees follow
  the GF formalism, and the types follow the Coq formalism. The
  converter itself is a Haskell Program, which implements a dynamic
  semantics and comprises the bulk of our system.
\item A number of type-theoretical combinators, that encode aspects of NL semantics which have no influence on the dynamic
  part. Such aspects include, e.g.,  the treatment of adjectives
  (intersective, subsective, etc.) and adverbs (veridical or not).
\end{enumerate}

@@

\paragraph{ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.

For example, in \ref{ex:acd}, the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context.
\paragraph{definites} A naive way to handle definites is an
existential (or sigma). However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$∀x. person(x) → ∃y. dog(y) ∧ pet(x,y)$.

>>>>

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types. Coq is one of the leading proof assistants. It
has famously been instrumental in formalising a proof of the
four-color theorem \citep{Gonthier:2008}, a proof of the odd order
theorem \citep{Gonthier:2013}. Coq is a very powerful reasoning engine
that makes it fit for the task of NLI, when the latter is formalized
as theorem proving task. It supports
notably dependent typing and subtyping, which are instrumental in
expressing NL semantics.

@@

Our system consists of two main parts.
\begin{enumerate}[noitemsep]
\item A converter from syntax trees to types. The syntax trees follow
  the GF formalism, and the types follow the Coq formalism. The
  converter itself is a Haskell Program, which implements a dynamic
  semantics and comprises the bulk of our system.
\item A number of type-theoretical combinators, that encode semantical
  aspects which have no influence on the dynamic part. Such aspects
  include the treatment of adjectives (intersective, subsective, etc.)
  and adverbs (veridical or not).
\end{enumerate}

@@

\paragraph{ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.
%
For example, in \ref{ex:acd}, the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context.

\paragraph{definites} A naive way to handle definites is an
existential (or sigma). However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$∀x. person(x) → ∃y. dog(y) ∧ pet(x,y)$.
